---
title: 'CIND 123 - Assignment #3'
output:
  word_document: default
  pdf_document: default
---

This assignment questions make use of data that is provided by the
`ISwR` package.

```{r}
library(ISwR)
```

## Question 1 

In this question you will explore the airquality dataset available in the datasets library in the ISwR package.

a) Display the first 6 rows of the airquality dataset.

```{r}
data("airquality")
head(airquality,6)

```

b) Display the type of each column of the airquality dataset, use only one function in R to do so.

```{r}
sapply(airquality,class)
```

c) Use a histogram to assess the normality of the `Ozone` variable.(In order to get the output diagram inserted in your answer use attach(dataframe name)) 
```{r}
attach(airquality)
hist(Ozone)
```
d) Does it appear normally distributed? 
```{r}
# No the data is not normally distributed. It is right skewed
```
e) Create a boxplot which shows the distribution of `Ozone` in each month.Use different colors for each month.
```{r}
library(ggplot2)
g<-ggplot(airquality,aes(x=as.factor(airquality$Month),y=airquality$Ozone))
g+geom_boxplot(outlier.colour = "red",aes(colour=airquality$Month,fill=airquality$Month))+scale_fill_distiller(palette = "Reds")+labs(x="Months",y="Ozone Level",title="Boxplot of Ozone by month")+theme_classic()

```
f) Create one scatter plot matrix of the numeric variable (Ozone, Solar.R,Wind,Temp) within the airquality dataset.
(Hint investigate pairs())

```{r}
pairs(airquality[,1:4])

```

## Question 2 
a)Use simulation to estimate the mean and variance of a binomial random variable with n = 18 and p = 0.76. 

```{r}
x<-rbinom(100,18,prob=0.18)
x
mean(x)
var(x)

```

b) Calculate the values using the theroy (state the value and the equation in your answer), compare the values you get with the values you got in (a), write one sentence summerizing the comparison.

```{r}
# n<-18
#p<-0.18
# Mean = n*p = 3.24 Which is approximate to mean we got above
# Variance = n*p*(1-p) = 2.6568 which is almost equal to what we got above

# The values are almost same. 

```

## Question 3  
a) Estimate the mean and variance of a Poisson random variable whose mean is 7.2 by simulating 10,000 Poisson random numbers.
```{r}
x<-rpois(10000,7.2)
mean(x)
var(x)
```
b) Compare the mean value you got in (a), with the one stated in the question. Write one sentence summarizing the comparison.

```{r}
#Here, Lembda = 7.2 , Hence the mean = 7.2 , We got almost same number with the formula above mean(x)
# Also, in Poisson distribution Var = Lembda = 7.2 and we got almost same number with the number above var(x)
```
## Question 4  
Simulate 100 realizations of a normal random variable having a mean of 51 and a standard deviation of 5.2.
```{r}
rnorm(100,51,5.2)
```

END of Assignment #3.



