---
title: 'CIND 123 - Assignment #4'
output:
  word_document: default
  pdf_document: default
---

This assignment makes use of pakcage "RCurl", accordingly carry out the following:
```{r load_packages}
#install.packages("RCurl")
library(RCurl) 
```
First we read the computers.csv file and load the price using the following: 
```{r}
u <- getURL("http://vincentarelbundock.github.io/Rdatasets/csv/Ecdat/Computers.csv")
cprices <- read.csv(text =u)
```
1) Display the first 6 rows of cprices and make note of all the variables.
```{r}
attach(cprices)
head(cprices,6)

```
2) Calculate the mean, variance and standard deviation of price by omitting the missing values, if any.
```{r}
mean(cprices$price, na.rm = TRUE)
sd(cprices$price, na.rm = TRUE)
var(cprices$price, na.rm = TRUE)

```
3) Use `ram` to predict price and build a univariate linear regression model, display a summary of your model indicating Residuals, Coefficients..etc.
```{r}
model1<-lm(price~ram,data = cprices)
summary(model1)

```
4) Based on the output of your model, predicted the expected price when ram is set to 8 MB
```{r}
attach(cprices)
newdata=data.frame(ram = 8)
predict(model1,newdata,interval="prediction")

```
5) Find Pearson correlation between hard disk and speed.
```{r}
cor(hd,speed,method = "pearson")
```
6) Write the correlation matrix of the variables: price, speed, hd and ram.
```{r}
cprices1<-cprices[,2:5]
cor(cprices1)
library(corrplot)
corrplot(cor(cprices1), method = "number")
```
7) Visualize the correlation of the numeric columns in the computer prices dataset.
```{r}
cprices<-cprices[,c(1,2,3,4,5,6,10,11)]
corrplot(cor(cprices),method = "circle")

```
END of Assignment #4.



