---
title: "Assignment3"
author: "Harnoor Rangi"
date: '2017-08-10'
output: word_document
---
#Reading Url into R

```{r}
winequality<-read.csv(url("http://archive.ics.uci.edu/ml/machine-learning-databases/wine-quality/winequality-white.csv" ), header = TRUE, sep = ";")
attach(winequality)
```

#Question 1: Check data characteristics. Is there missing data? Prepare the data for analysis.


```{r}
#Checking for missing values

sapply(winequality, function(x) sum(is.na(x)))

summary(winequality)
sapply(winequality, class)
str(winequality)
```


#Question 2: What is the correlation between the attributes other than wine quality?


```{r}
par(mfrow = c(1,1))
cor.white <- cor(winequality[-c(12,13)])
cor.white
library(corrplot)
corrplot(cor.white, method = 'number')
```


#Question 3: Graph the frequency distribution of wine quality.


```{r}
library(ggplot2)
qplot(winequality$quality, data=winequality, main=" frequency dist. of Wine Quality",xlab="Quality", ylab="Frequency") 
```


#Question 4: Reduce the levels of rating for quality to three levels as high, medium and low.


```{r}
int <- cut(winequality$quality, c(2,5,6,9))
levels(int) <- c("low", "medium", "high")
label <- levels(int)
winequality["labels"] <- NA
winequality["labels"] <- int
white <- winequality[-c(12)]
```


#Question 5: Normalize the data set.


```{r}

w<-winequality[,c(12,13)]
winequality<-winequality[,c(-12,-13)]

doit <- function(x) {(x - min(x, na.rm=TRUE))/(max(x,na.rm=TRUE) -
                                                 min(x, na.rm=TRUE))}
normed <- as.data.frame(lapply(winequality, doit))
normed[,c(12,13)]<-w

```

#Question 6: Divide the data to training and testing groups.


```{r}

dim(normed)  

#Sample Indexes


indexes <- sample(1:nrow(normed), size=0.7*nrow(normed))

# Split data


train <- normed[indexes,]
dim(train)  
test <- normed[-indexes,]
dim(test) 
```


#Question 7: Use the KNN algorithm to predict the quality of wine using its attributes.


```{r}

train_labels <- train$labels
test_labels <- test$labels

train.set_new <- train[,c(-12,-13)]
test.set_new <- test[,c(-12,-13)]



library("class")
library("gmodels")
knn_prediction <- knn(train = train.set_new, test = test.set_new, cl = train_labels, k = 5)
cross <- CrossTable(x=test_labels, y=knn_prediction, prop.chisq=FALSE)
```

#Question 8: Evaluate the model performance.


```{r}
eva <- data.frame(cross$t)
evalKNN <- eva
dim(evalKNN)

x <- c(eva$Freq[1] + eva$Freq[5] + eva$Freq[9])
y <- x/1470
y
```